Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-04 mu/article/article.tex
Starting plots modifications.

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

\textbf{Alt structure.}
% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d}
\end{figure}

>>>>

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    response for C$_{16}$H$_{8}$-up structure. The local maxima responses zones
    are localized for an energy range from 1.95\,eV to 2.00\,eV and for
    polarization angles of the incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

\textbf{Alt structure.}
% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    responses for C$_{16}$H$_{8}$-alt structure. The maxima responses zones are
    localized for an energy range from 0.90\,eV to 0.93\,eV and for polarization
    angles of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d}
\end{figure}
